---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

### Load libraries
library(tidyverse)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(wesanderson)

```

#Preparation

Read in data and tidy up dataset

```{r ReadIn,  echo = FALSE}
#Get the data
source("scripts/calculateES.R")

```

```{r Preprocess, echo = FALSE}

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31)


db_ET$collapse <- paste(db_ET$study_ID, db_ET$expt_num, db_ET$same_infant, sep = "_")

#Split into correct and MP database

db_ET_correct <- db_ET[db_ET$is_correct=="1",]
db_ET_MP <- db_ET[db_ET$is_mp=="1",]

#collapse over nonindependent MP rows for a *general* MP effect


collapse_rows <- function(db){
  db$collapse <- paste(db$study_ID, db$expt_num, db$same_infant, sep = "_")
  
  for(independent in unique(db$collapse)){
    if(length(db[db$collapse==independent])>1){
      sub = db[db$collapse==independent, ]
      sub$d_calc <- median(sub$d_calc)
      sub$d_var_calc <- median(sub$d_var_calc)
      sub$g_calc <- median(sub$g_calc)
      sub$g_var_calc <- median(sub$g_var_calc)
      sub$corr_imputed <- median(sub$corr_imputed)
      db <- db[!(db$collapse==independent),]
      db <- rbind(db, sub[1,])
    }
  }
  return(db)
}


#db_ET_correct = collapse_rows(db_ET_correct)

#db_ET_MP = collapse_rows(db_ET_MP)

#remove outliers, for now we have none, though
db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]

db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]


# make sure that both correct and mispronounced conditions are considered in descriptives

db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)

# need data set of unique short cite by expt_num
# in order to calculate total number of infants

# need data set of unique short cite by condition

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]
mix_co_mp <- dat[!duplicated(dat[c("short_cite", "word_correct_and_MP")]),]

```

# Plotting defaults

```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

```

# Descriptive data

The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.

The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

pub_info <- dat %>%
  group_by(publication_status) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(pub_info)

```

## Type of data on which we calculated effect sizes
The table below shows based on which data we calculated effect sizes.

```{r DescriptivesES, echo = FALSE}
#how did we calculate effect sizes?

es_info <- dat %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

kable(es_info)
#table(dat$es_method, dat$short_cite)
# only missing from:
# Bailey & Plunkett (2002) <- crazy old data
# Renner (2017) <- just finished phd
# Tamasi (2016) <- standard deviations are wrong
#table(db_ET_MP$es_method)

```

## Number of unique infants

```{r DescriptivesInfnum, echo = FALSE}

infnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "n_1")]
infnum_info <- unique(infnum_info)

number_of_infants <- sum(infnum_info$n_1)


```

The database contains data from `r number_of_infants` unique infants.

## Number of unique experimental conditions

```{r DescriptivesExpCond, echo = FALSE}

condnum_info <- dat[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
condnum_info <- unique(condnum_info)

number_of_cond <- nrow(condnum_info)


```

The database contains data from `r number_of_cond` unique experimental conditions


## Type of comparison of the time-course data calculated
We also have different ways of comparison of the time-course data, as the next table shows.

```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))


comparison_info <- db_ET_correct %>%
  group_by(within_measure_descriptive) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())


kable(comparison_info)
#table(db_ET_MP$es_method)
```

## Type of distractor
This is a summary of the type of distractor used in an experiment

```{r DescriptivesDISTRACT, echo = FALSE}
#What kind of distractor was used?

distr_info <- distract_dat %>%
  group_by(object_pair) %>%
  summarize(count = n())


kable(distr_info)

```

## Whether word was pronounced both correctly as well as mispronounced
This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

```{r DescriptivesCoMp, echo = FALSE}
#What kind of distractor was used?

mix_info <- mix_co_mp %>%
  group_by(word_correct_and_MP) %>%
  summarize(count = n())


kable(mix_info)

```

## Size of analysis time window

Where possible, we noted the time window for analysis. First, let's look at the offset (in milliseconds) after the start of the word, i.e. the begin of a give analysis window for a naming effect

```{r TimeWindowOffset}
offset_info <- time_wind_dat %>%
  group_by(offset) %>%
  summarize(count = n())


kable(offset_info)

```

## Duration of post naming window
Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

```{r TimeWindowduration}
duration_info <- db_ET_correct %>%
  group_by(post_nam_dur) %>%
  summarize(count = n())


kable(duration_info)

```

In summary, we see little consistency in analysis methods of comparable studies looking at naming and mispronunciation effects. 


## Mispronunciation Sensitivity in the youngest ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

```{r YoungAge, echo = FALSE}
youngest <- subset(dat, min_age_1 < 365)

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

```


# Meta-Analysis

## Main Mispronunciation Sensitivity Effects

### Correct object identification effect

```{r MAcorrect}

rma_correct = rma.mv(g_calc, g_var_calc, data = db_ET_correct, random = ~ collapse | short_cite)

summary(rma_correct)

#kable(round(coef(summary(rma_correct)), 2))

```

### Mispronunciation object identification effect

```{r MAMP}

rma_MP = rma.mv(g_calc, g_var_calc, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_MP)


```


### Mispronunciation Sensitivity effect

```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)
  
rma_MPeffect <- rma.mv(g_calc, g_var_calc, mods = ~condition, data = dat, random = ~ collapse | short_cite)
  
summary(rma_MPeffect)  

rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)
  
summary(rma_MPeffect_1)  


```


## Main Mispronunciation Sensitivity Effects with Age Moderators

### Correct object identification effect with age moderator

```{r MAcorrect_age}

rma_correct_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_correct, random = ~ collapse | short_cite)

summary(rma_correct_age)
#kable(round(coef(summary(rma_correct_age)), 2))


```

### Mispronunciation object identification effect with age moderator


```{r MAMP_age}

rma_MP_age = rma.mv(g_calc, g_var_calc, mods = ~age.C, data = db_ET_MP, random = ~ collapse | short_cite)

summary(rma_MP_age)
```

### Mispronunciation Sensitivity effect with age moderator

```{r MPEffect_age}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

dat <- bind_rows(db_ET_correct, db_ET_MP)

rma_MPeffect_age <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition, data = dat, random = ~ collapse | short_cite)
  
summary(rma_MPeffect_age)  


```

## Plotting Mispronunciation Effect

### Plot Mispronunciation Effect by Age (color)

```{r PlotMPEffect}

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
  
p

min(dat$mean_age_1/30.44)
max(dat$mean_age_1/30.44)

#ggsave("figures/AgeEffect_log.jpg", p,height= 7,width= 6)



  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 600, height = 400, units = "px")

  p
  
  dev.off()
  


```

### Plot Mispronunciation Effect by Age (bw)

```{r PlotMPEffect_BW}


p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
             show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_color_grey()+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)

```


## Correlation MP effect and Vocabulary

First, let's take a look at which vocabulary data we have available.

```{r VocabularyData}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n())
  
kable(vocab_info)

```

We have 17 correlations, roughly evenly divided between comprehension and production data. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.


```{r ComprehensionMeta}
#we're relying on the library meta function metacor
compr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_comprehension) & r_comprehension > -1)

metacor(cor=r_comprehension, n=n_1, studlab = short_cite, data = compr, sm = "COR")
```

```{r ProductionMeta}
#we're relying on the library meta function metacor
prodr  <- subset(db_ET_correct, !is.na(db_ET_correct$r_production) & r_production < 1)

metacor(cor=r_production, n=n_1, studlab = short_cite, data = prodr, sm = "COR")
```

## Number of Features Changed

### Number of features

Size of mispronunciation, measured in features changed


```{r NFeatures}

db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = db_ET_MPf, random = ~collapse | short_cite)
 
 
summary(rma_NFeatures)

```

### Number of features subset to age range
Size of mispronunciation, measured in features changed


```{r NFeatures_subset}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature), data = dat_f, random = ~collapse | short_cite)
 
 
summary(rma_NFeatures_agesub)

```

### Number of features with condition moderator

```{r NFeaturesCondition}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*condition, data = dat_f, random = ~collapse | short_cite)
 
 
summary(rma_NFeatures)

```

### Number of features with age moderator

```{r NFeatures_age}

db_ET_MPf  <- subset(db_ET_MP, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C, data = db_ET_MPf, random = ~collapse | short_cite)
 
 
summary(rma_NFeaturesAge)
```


### Number of features with condition and age moderators

```{r NFeaturesCondition_age}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")


rma_NFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(n_feature)*age.C*condition, data = dat_f, random = ~collapse | short_cite)
 
 
summary(rma_NFeaturesAge)
```

### Features changed with age moderator, subset to same age range

```{r FeatureAgeRangeSubset}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_FeatureAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
  
summary(rma_FeatureAgeS)  


#rma_FeatureS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(n_feature), data = dat_fage, random = ~ collapse | short_cite)
  
#summary(rma_FeatureS)  

```

## Plotting number of Features Changed

### Plot number of Features

```{r PlotFeatEffect}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
                         ifelse(dat_f$n_feature == 2, "two",
                                ifelse(dat_f$n_feature == 3, "three",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

dat_f <- subset(dat_f, feat_cat != "none")


p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat.jpg", p)

```
### Plot number of Features subsetted for age

```{r PlotFeatEffect_agesubset}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
  geom_point(aes(size = weights_g, shape = Features_changed),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_feat_agesub.jpg", p)

```

### Plot number of Features subsetted for age Boxplot

```{r PlotFeatEffect_agesubset_boxplot}

dat_f <- subset(dat, n_feature == "0" | n_feature == "1" |
                n_feature == "2" | n_feature == "3")

mf <- subset(dat_f, n_feature == "3")
min_age <- min(mf$mean_age_1)
max_age <- max(mf$mean_age_1)

dat_fage= dat_f%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$feat_cat <- ifelse(dat_fage$n_feature == 1, "1-feature",
                         ifelse(dat_fage$n_feature == 2, "2-feature",
                                ifelse(dat_fage$n_feature == 3, "3-feature",
                                       ifelse(dat_fage$n_feature == 0, "correct", "none"))))

dat_fage <- subset(dat_fage, feat_cat != "none")

dat_fage$Features_changed <- factor(dat_fage$feat_cat, levels = c("correct", "1-feature", "2-feature", "3-feature"))

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat_fage, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

p

ggsave("figures/AgeEffect_log_feat_agesub_noage.jpg", p)

```

## Type of MP: Vowel, consonant, or tone

### Type of MP: Vowel, consonant, or tone

```{r MPtype}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )



rma_TypeFeaturesMP <- rma.mv(g_calc, g_var_calc, mods = ~type_feature, data = db_MP_type, random = ~collapse | short_cite)
 
 
summary(rma_TypeFeaturesMP)

```

### Type of MP: Vowel, consonant, or tone with age moderator


```{r MPtype_age}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )


rma_TypeFeaturesMPAge <- rma.mv(g_calc, g_var_calc, mods = ~type_feature*age.C, data = db_MP_type, random = ~collapse | short_cite)
 
 
summary(rma_TypeFeaturesMPAge)
```

### Type of MP: Vowel, consonant, or tone with condition moderator

```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))


rma_TypeFeatures <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*condition, data = dat_type, random = ~collapse | short_cite)
 
 
summary(rma_TypeFeatures)

```


### Type of MP: Vowel, consonant, or tone with age and condition moderator

```{r MPtypeCondition_age}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))


rma_TypeFeaturesAge <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*age.C*condition, data = dat_type, random = ~collapse | short_cite)
 
 
summary(rma_TypeFeaturesAge)
```

### Type of MP with language family moderator

```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")

dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")

rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family, data = dat_type_sub, random = ~collapse | short_cite)
 

summary(rma_TypeFeatures_Lang)
```


### Type of MP with language family and condition moderators

```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

dat_type$lang_family = ifelse(dat_type$native_lang=="American English" | dat_type$native_lang=="British English" | dat_type$native_lang=="Dutch" |
dat_type$native_lang=="Danish" | dat_type$native_lang=="Swedish" |
dat_type$native_lang=="English" | dat_type$native_lang=="German", "Germanic", ifelse(dat_type$native_lang == "French" | dat_type$native_lang == "Catalan" | dat_type$native_lang == "Spanish" | dat_type$native_lang == "Catalan-Spanish" | dat_type$native_lang == "Swiss French", 
                                "Romanic", "Sino-Tibetian"))

dat_type_sub <- subset(dat_type, lang_family != "Sino-Tibetian")
dat_type_sub$lang_family <- as.factor(dat_type_sub$lang_family)



rma_TypeFeatures_Lang <- rma.mv(g_calc, g_var_calc, mods = ~relevel(type_feature, "none")*lang_family*condition, data = dat_type_sub, random = ~collapse | short_cite)
 

summary(rma_TypeFeatures_Lang)

```

## Plotting MP type: Consonant, Vowel, or Tone?

### Plot MP type: Consonant, Vowel, or Tone?

```{r PlotCVEffect}


p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = type_feature),show.legend=FALSE) + 
  facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_CV.jpg", p)
```

### Plot Language Family by MP type: Consonant, Vowel, or Tone?

```{r PlotCVEffect_Lang}


p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p


ggsave("figures/LangFamily_CV.jpg", p)
```


## Distractor Familiarity (familiary, unfamiliar) 

```{r DistractorType}

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
  
summary(rma_Distractor)  

```

### Distractor Familiarity with condition moderator

```{r DistractorTypeCondition}

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
  
summary(rma_Distractor)  

```

### Distractor Familiarity with age moderator
```{r DistractorTypeAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
  
summary(rma_DistractorAge)  

```

### Distractor Familiarity with age and condition moderators
```{r DistractorTypeConditionAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)
  
summary(rma_DistractorAge)  

```

### Distractor Familiarity with condition moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset_condition}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
  
summary(rma_DistractorAgeS)  

```

### Distractor Familiarity with age and condition moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset_agecondition}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_DistractorAgeS <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)
  
summary(rma_DistractorAgeS)  

```

### Plotting Distractor Familiarity

### Plot Distractor Familiarity

```{r PlotDistFamEffect}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_fam.jpg", p)

```

### Plot Distractor Familiarity (w/o age)

```{r PlotDistFamEffect_NoAge}

dat$condition_label = ifelse(dat$condition==1, "correct", "MP")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat, aes(dist_code, g_calc, color = condition_label)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=wes_palette(name="Darjeeling"))+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Distractor Familiarity") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")
p



ggsave("figures/Distractor_fam_log.jpg", p)


```

### Plot Distractor Familiarity (w/o age, subset to age range)

```{r PlotDistFamEffect_NoAge_AgeMatch}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_age= dat%>%
  filter(mean_age_1>min_age&mean_age_1<max_age)

dat_age$condition_label = ifelse(dat_age$condition==1, "correct", "mispronunciation")
dat_age$dist_code <- ifelse(dat_age$object_pair == "familiar_familiar", "Familiar Distractor", "Unfamiliar Distractor")

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat_age, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  facet_grid(.~dist_code) +
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

p

ggsave("figures/AgeMatch_Distractor_fam_log.jpg", p)

```


### Plot Distractor Familiarity by age subsetted for age

```{r PlotDistFam}

mf <- subset(dat, object_pair=="familiar_novel")
min_age <- min(mf$mean_age_1)

mf <- subset(dat, object_pair=="familiar_familiar")
max_age <- max(mf$mean_age_1)

dat_fage= dat%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

dat_fage$dist_fam <- ifelse(dat_fage$object_pair == "familiar_novel", "Novel Distractor", "Familiar Distractor")

# Color Blind palette:
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p <- ggplot(dat_fage, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_fam),show.legend=FALSE) + 
  facet_grid(.~dist_fam)+
    scale_colour_manual(values=cbPalette)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_DistFam_agesub.jpg", p)

```

## Position of Mispronunciation (onset, medial)

```{r Location}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)
 
 
summary(rma_Location)

```

### Position of Mispronunciation with age moderator

```{r Location_age}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")


rma_LocationAge <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
 
 
summary(rma_LocationAge)
```

### Position of Mispronunciation with condition moderator

```{r Location_condition}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")


rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)
 
 
summary(rma_LocationCondition)
```

### Position of Mispronunciation with age and condition moderators

```{r Location_condition_age}
#table(db_ET_MP$mispron_location)

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")


rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)
 
 
summary(rma_LocationCondition)
```

## Plotting Position of Mispronunciation
```{r PlotPositionEffect}

#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
#                mispron_location == "offset")

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")

p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
  facet_grid(.~mispron_location)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_position.jpg", p)

```

## Distractor Overlap

```{r DistractorOverlap}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
  
summary(rma_DistractorOverlap)  

```

### Distractor Overlap with age moderator

```{r DistractorOverlap_age}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
  
summary(rma_DistractorOverlap)  

```


### Distractor Overlap with condition moderator

```{r DistractorOverlap_condition}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
  
summary(rma_DistractorOverlap)  

```

### Distractor Overlap with age and condition moderators

```{r DistractorOverlap_age_condition}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)
  
summary(rma_DistractorOverlap)  

```

## Plotting Distractor Overlap

```{r PlotDistOverlapEffect}


p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
  facet_grid(.~distractor_overlap)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)

```



## Language effect

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```


### Language effect with age moderator

```{r LanguageEffectAnalyses_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```

### Language effect with condition moderator


```{r LanguageEffectAnalyses_condition}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```

### Language effect with age and condition moderators


```{r LanguageEffectAnalyses_condition_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```

## Plotting Language Effect
```{r PlotLanguageEffect}


dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
  facet_grid(.~lang_family)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_language.jpg", p)

```
