---
title             : "The development of infants' responses to mispronunciations - a Meta-Analysis"
shorttitle        : "Mispronunciation Meta-Analysis"

author: 
  - name          : "Katie Von Holzen"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "45, rue des Saints-Peres, 75006 Paris, France"
    email         : "katie.m.vonholzen@gmail.com"
  - name          : "Christina Bergmann"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Laboratoire Psychologie de la Perception, Université Paris Descartes"
  - id            : "2"
    institution   : "LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University"



author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

abstract: >
  Enter abstract here (note the indentation, if you start a new paragraph).
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library("papaja")
```

outline christina:

Main question: How do reactions to mispronunciations change over age, because we (1) know that infants notice MPs and (2) that their processing and representations mature. 

Theory one: Infants develop more precise word- and sound-level representations. (Who would claim that for example?)  
Prediction: They become MORE sensitive to MPs.  

Theory two: Infants can resolve MPs better as they get older, because they realize that the competitor is not the target. (kv: this comes from the way we test mispronunciation? familiar vs unfamiliar distractor? maybe that can be a thread throughout the paper) 
Prediction: They become LESS sensitive to MPs and this should be most pronounced with familiar objects as competitors.  (yes)

Theory three: Infants don't change how they process words over the time range covered, they just become more efficient information processors overall.  
Prediction: The effect sizes go up as infants mature but the MP effect (difference between correct and mp) remains constant.   

Thus, a meta-analysis offers unique insights into theoretically crucial questions of how infants process words and phonemes. 

```{r Notes as comments}


# moving notes from Christina here
#[Christina: Katie, I am adding the next sentences to set up a general analysis of age effects, but correct anything that is wrong]
#However, whether infants' sensitivity to mispronunciations increases or decreases over time is yet unknown [?????] and can serve to distinguish competing models of early language acquisition. If infants start out as overly cautous and specific language processors, their mispronunciation sensitivity should be larger at younger ages, as only later in life infants learn to contend with variability in their input [Add some references to Cathy Best and others here? Cite a concrete model? Not sure who says what any more]. 

#Alternatively, infants may start out with lexical representatins that are overly broad and might then reconsider and refine those representations as language experience accumulates [add references here too, I think that's sort of what Primir says, right?]. In this latter case, one would predict an increase in mispronunciation sensitivity as infants mature and become more competent language users. 

#A third possibility is that infants' overall language processing becomes more efficient, but that their sensitivity to mispronunciations does not change -- accross infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the effect would not change.


```


As infants develop into toddlers during their second and third years they learn new words in earnest while simultaneously refining their knowledge about the sounds that make up these words. Before children can correctly pronounce a word, they already show evidence of sensitivity to slight variations in the phonological form of that word. This *mispronunciation sensitivity* reflects the specificity with which infants represent the phonological information of familiar words and are sensitive to changes in this phonological information. As infants continue to develop into expert language users, their language processing matures and becomes more efficient. In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonetic details that differentiate words in their native language. In this paper, we aggregate and analyze the almost 20 years of literature investigating mispronunciation sensitivity in infants in an attempt to uncover the characteristics and trajectory of its development.

  At the turn of the millenia, infant langauge acquisition researchers had established that during their first year of life, infants are sensitive to changes in the phonetic detail of newly segmented words (Jusczyk & Aslin, 1995) and learned minimal pairs (Stager & Werker, 1997). Furthermore, when presented with image pairs, children fixate on one image upon hearing its label (Swingley & Fernald, 1998; Fernald, Pinto, Swingley, Weinberg, & McRoberts, 1998). Swingley and Aslin (2000) were the first to tie these lines of research together and investigate mispronunciation sensitivity in infant familiar word recognition: Children aged 18 to 23 months learning American English were presented with pairs of images (e.g. baby, dog) and their eye movements to each image were coded offline. On "correct" trials, children heard the correct label for one of the images (e.g. baby). On "mispronounced" trials, children heard a mispronounced label of one of the images (e.g. vaby). Mean proportion of fixation to the target image (here: a baby) was calculated for both correct and mispronounced trials by dividing the target looking time by the sum of total looking time to both target and a distractor (proportion of target looking or PTL). Mean fixations in correct trials were significantly greater than that of mispronounced trials, although looks to the target were significantly greater than chance in both types of trials. We refer to this pattern of a difference between looks to correct and mispronounced words as *mispronunciation sensitivity* and of looks to the target image above chance as *recognition*. Swingley and Aslin (2000) concluded that already before the second birthday, children represent words with sufficient detail to be sensitive to mispronunciations.  

  The study of Swingley and Aslin (2000) as well as subsequent studies examining mispronunciation sensitivity address two complementary concepts in early phonological development: *phonological consistency* and *phonological distinctiveness*. Phonological consistency is the ability to accept phonological variation across different instances of a word, as long as the variation does not compromise the overall identity of the word. For example, different speakers - particularly across genders and accents - produce the same word with notable acoustic variation, although the word remains the same. In contrast, phonological distinctiveness describes the ability to differentiate between words that are phonologically similar, such as bad/bed or cat/rat. To successfully recognize words, infants must therefore simultaneously use both phonological consistency and distinctiveness to determine where phonological variation is appropriate and where it violates a word's identity.

  In the current study, we focus on infants' ability to correctly apply the principles of phonological distinctiveness and consistency by using a meta-analytic approach to investigate mispronunciation sensitivity. Considering that infants are sensitive to mispronunciations and that, in general, their processing matures with development, we examine the shape of mispronunciation sensitivity development. [Ch: Adding this] There are three distinct possibilities how mispronunciation sensitivity might change over developmen, which are respectively predicted by theoretical accounts and supported by single studies. By aggregating all available evidence using meta-analysis, we can examine developmental trends making use of data from a much larger and diverse sample of infants. Before we outline the meta-analytical approach in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.
  
  Young infants may begin cautiously in their approach to word recognition, rejecting any phonological variation in familiar words and only later learning to accept appropriate variability. According to the Perceptual Attunement account, this describes a shift away from specific native phonetic patterns to a more mature understanding of the abstract phonological structure of words (Best 1994, 1995). This shift is predicted to coincide with the vocabulary spurt around 18 months, and is therefore related to vocabulary growth. In this case, we would expect the size of mispronunciation sensitivity to be larger at younger ages and decrease as the child matures and learn more words, although children continue to detect mispronuncaitions.
Indeed, young infants are less likely than older infants to demonstrate recognition of familiar words (Best, Tyler, Gooding, Orlando, & Quann, 2009; Mulak, Best, & Tyler, 2013) or learn new words (Schmale, Hollich, & Seidl, 2011) from accented speakers.

  In contrast, young infants may instead begin with phonologically broad representations for familiar words and only refine their representations as language experience accumulates. PRIMIR (Processing Rich Information from Multidimensional Interactive Representations; Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) describes the development of phonemic categories emerging as the number of word form-meaning linkages increase. Vocabulary growth, therefore, promotes more detailed phonological representations in familiar words. Following this account, we may predict an increase in mispronunciation sensitivity as infants mature and add more words to their growing lexicon. 
  
  Finally, sensitivity to mispronunciation may not be modulated by development at all. Infants' overall language processing becomes more efficient, but their sensitivity to mispronunciations may not change. Accross infancy and toddlerhood, mispronunciations would thus be detected and lead to less looks at a target than correct pronunciations, but the size of this effect would not change, nor be related to vocabulary size.

  Research following the study by Swingley and Aslin (2000) has extended mispronunciation sensitivity to infants as young as 12 months (Mani & Plunkett, 2010), indicating that from early stages of the developing lexicon onwards, infants can and do detect mispronunciations. Regarding the change in mispronunciation sensitivity over development, however, only a handful of studies have compared more than one age group on the same mispronunciation task. For example [Ch: not sure what this is an example of], Swingley and Aslin (2000) tested infants from 18 to 23 months.  They found that age correlated with target fixations for both correct and mispronounced labels, whereas the difference between the two (mispronunciation effect) did not. This suggests that as children develop, they are more likely to look at the target in the presence of a mispronounced label and that age is not related to mispronunciation sensitivity. A similar response pattern has been found for British English learning infants aged between 18 and 24 months (Bailey and Plunkett, 2002) as well as younger French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, & Frauenfelder, 2012). These studies award support to the prediction that mispronunciation sensitivity does not change with development.

  In contrast, other studies have found evidence for a change in mispronunciation sensitivity as children develop. More precisely, the difference in target looking for correct and mispronounced trials is smaller in younger infants and grows as infants develop. Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British English; although all three groups were sensitive to mispronunciations, 15-month-olds showed a less robust sensitivity. An increase in sensitivity to mispronunciations has also been found from 20 to 24 months (van der Feest & Fikkert, 2015) and 18 to 15 months [Ch: ???? 15 to 18???] (Altvater Mackensen et al., 2013) in Dutch infants, as well as German infants from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest and Fikkert (2015) found that sensitivity to specific kinds of mispronunciations develop at different ages depending on language infants are learning. In other words, the native language constrains which *kinds* of mispronunciations infants are sensitive to first, and that as infants develop, they become sensitive to other mispronunciations. These studies award support to the prediction that mispronunciation sensitivity improves with development.

  Finally, one study has found evidence for infants to become *less* sensitive to mispronunciations as children develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with mispronunciations varying in the number of features changed (see below for a discussion of the role of features). 18-month-olds were sensitive to mispronunciations, regardless of the number of features changed. 24-month-olds, in contrast, fixated the target image equally for both correct and 1-feature mispronounced trials, although they were sensitive to larger mispronunciations. In other words, for 1-feature mispronunciations at least, sensitivity decreased from 18 to 24 months, providing support to the prediction that mispronunciation sensitivity may decrease with development.

  Why would mispronunciation sensitivity change as infants develop, and would it increase or decrease? One hypothesis is related to vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and PRIMIR (Curtin & Werker, 2007; Werker & Curtin, 2005; Curtin, Byers-Heinlein, & Werker, 2011) accounts situate a change in mispronunciation sensitivity occuring along with an increase in vocabulary size, particulary with the vocabulary spurt at about 18 months. Knowing more words helps infants shift their focus to the relevant [Ch: changed this from ingredients] phonetic dimensions needed for word recognition. On the one hand, a smaller lexicon does not require full specification to differentiate between words; as more phonologically similar words are learned, so does the need to have fully detailed representations for those words (Charles-Luce & Luce, 1995). On the other hand, a growing vocabulary is also related to more experience or familiarity with words, which may sharpen the detail of their representation (Barton, 1980).
  
  Yet, the majority of studies examining a potential association between mispronunciation sensitivity and vocabulary size have found no relationship [Ch: Tricky, might also be a false negative or a small relationship, maybe reformulate: have concluded that there is no relationship] (Swingley & Aslin 2000; 2002; Bailey & Plunkett, 2002; Zesiger, Lozeron, Levy, & Frauenfelder, 2012; Swingley, 2009; Ballem & Plunkett, 2005; Mani & Plunkett, 2007; Mani, Coleman, & Plunkett, 2008). One notable exception comes from Mani and Plunkett (2010: keps and tups). Here, 12-month-old infants were divided into a low vocabulary and high vocabulary group based group median vocabulary size. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations. Taken together, although recieving considerable support from theories of phono-lexical processing in language acquisition, there is very little evidence for a role of vocabulary size in mispronunciation sensitivity. In our current meta-analysis, we include the relationship between mispronunciation sensitivity and vocabulary size to further disentangle the disconnect between theory and experimental results. [Ch: The disconnet is not quite clear to me right now.]

  Next to this core theoretically relevant investigation of the shape of mispronunciation sensitivity as infants develop, we can also address open questions regarding differences in experiment design and whether changes in procedure and stimuli tap into significantly different aspects of infants' ability to detect mispronunciations. 

  In designing their mispronunciation stimuli, Swingley and Aslin (2000) chose consonant mispronunciations that were likely to confuse adults (Miller & Nicely, 1955). Subsequent research has settled on systematically modulating phonemic features to achieve mispronunciations of familiar words. The importance of controlling for the degree of phonological mismatch, as measured by number of features changed, is highlighted by studies that find graded sensitivity to both consonant (White & Morgan, 2008) and vowel (Mani & Plunkett, 2011) feature changes. In addition to number of features changed,  the type of feature changed may also play an important for mispronunciation sensitivity, as some acoustic characteristics provide more reliable cues than others (Mani, Coleman, & Plunkett, 2008; Mani & Plunkett, 2011).

  Although most research examining sensitivity to mispronunciations follows a similar design, there are some notable differences.  For example, Swingley and Aslin (2000) presented infants with pairs of familiar images, one serving as the labeled target and one as the unlabeled distractor. In contrast, White and Morgan (2008; see also Mani & Plunkett, 2011; Skorrupa et al., 2013; Swingley, 2016) presented infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied (Halberda, 2003; Markman, Wasow, & Hansen, 2003). Although mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared, the baseline preference for familiar compared to novel stimuli is thought to change as infants develop (Hunter & Ames, 1988).  In other words, in absentia of a label, infants may be more or less likely to fixate on an unfamiliar object. To account for inherent preferences to the target or distractor image, mispronunciation experiments typically compare the increase in fixations to the target image from a silent baseline to post-labeling or present the same yoked pairs of target and distractor images in in both a correct and mispronounced labelling context. [Ch: Do you want to bring up mutual exclusivity more explicitly here? I think it's fine the way you mention it, but we might say that this ability develops in the 2nd year as well - if I remember correctly.]

  Furthermore, when presenting infants with a familiar distractor image, some studies control from the phonological overlap between the labels for the target and distractor. For example, when examining sensitivity to a mispronunciation of the target word "dog", the vowel mispronunciation "dag" would be paired with a distractor image that shares onset overlap, such as "duck". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images (Fernald, Swingely, & Pinto, 2001). Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. The influence of distractor overlap also depends on the position of the mispronunciation in the word, which is typically at word onset, medial, or final positions. Models of spoken word processing place more or less importance on the position of a phoneme in a word.  The COHORT model (Marslen-Wilson & Zwisterlood, 1989) describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word.  In contrast, the TRACE model (McClelland & Elman, 1986) describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset mispronunciations. 
  
  TRACE has also been used to model infants' sensitivity to mispronunciation location (Mayor & Plunkett, 2014), finding that as lexicon size increases, so does sensitivity to onset mispronunciations, whereas medial mispronunciations do not experience similar growth. In early language acquisition, infants typically know more consonant compared to vowel onset words. When tested on their recognition of familiar words, therefore, younger infants would show greater sensitivity to onset mispronunciations, which are frequently consonant mispronunciations. That position of mispronunciation, and by correlation whether it is a consonant or vowel mispronunciation, plays a role in mispronunciation sensitivity is related to the theory that consonants carry more weight in lexical processing (C-bias; see Nazzi, Poltrock, & Von Holzen, 2016 for a recent review). In mispronunciation sensitivity, this would translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani & Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds (Højen et al., unpublished) demonstrate similar sensitivity to consonant and vowel mispronunciations. One study did find weak evidence for greater sensitivity to consonant compared to vowel mispronuciations (Swingley, 2016). The English-learning infants tested by Swingley were older than previous studies (mean age 28 months). In word learning, the C-bias has been found to develop later in English learning infants (Floccia, Nazzi, Delle Luche, Poltrock, & Goslin, 2014; Nazzi, Floccia, Moquet, & Butler, 2009). In the current meta-analysis, we attempt to synthesize studies examining sensitivity to consonant and vowel mispronunciations across different languages and ages to determine whether infants generally exhibit a C-bias in familiar word recognition.

  Finally, mispronunciation sensitivity in infants has been examined in many different languages, such as English, Spanish, French, Dutch, German, Catalan, Danish, and Mandarin Chinese (perhaps refer to table of papers here? this will have language background information [Christina says yessssss - A table of all studies included like Alex does here might work: https://osf.io/z7xn3/]). Infants learning different languages have different ages of acquisition for words in their early lexicon, leaving direct comparisons between languages within the same study difficult and as a result rare. In one series of studies, Ramon-Casas and colleagues (Ramon-Casas et al., 2009; Ramon-Casas & Bosch, 2010) tested both monolingual Spanish or Catalan and bilingual Spanish-Catalan on their detection of a vowel mispronunciation in familiar words. Both groups were sensitive to the vowel change when there was little overlap between the Spanish and Catalan labels of the familiar words (Ramon-Casas & Bosch, 2010), but only monolingual toddlers were sensitive to the vowel change in words that overlapped completely between Spanish and Catalan (Ramon-Casas et al., 2009). In this case, the comparison between Spanish and Catalan is relatively straightforward, as they share many phonologically overlapping words. This is not typically the case for most languages, where the phonology of the language differs, rendering equivalent mispronunciations in different languages almost impossible. By assessing evidence of mispronunciation sensitivity from many different languages using a meta-analytic approach, it is possible to compare the development of mispronunciation effect across languages.
  
  [Ch: Should we explain here why the meta-analytic approach is useful and important? This might be necessary. Do you want todraft sth?]

## Methods


[Christina: Rewriting this section]

The present meta-analysis was conducted with maximal transparency and reproducibility in mind. To this end, we provide all data and analysis scripts and open our meta-analysis up for updates (Tsuji, Bergmann, & Cristia, 2015???). In addition, we follow the  Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the corresponding information available as supplementary materials. (Moher, Liberati, Tetzlaff, Altman & PRISMAGroup, 2009). 


# Study Selection

We first generated a list of potentially interesting items to be included in our meta-analysis by consulting our private collections for publications containing the search term "infant mispronunciation". This yielded 38 items. An additional 63 items were included based on recommendations from experts in the field. After removing duplicates, we screened the title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the item examined familiar word recognition; (3) infants studied were under 36-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image in a eye tracked experiment. The final sample consisted of 20 journal articles, two proceedings papers, one thesis, and one unpublished report. We will refer to these 25 items collectively as papers. Table X provides an overview of all papers included in the present meta-analysis.

# Data Entry


The 25 published papers we identified as relevant were then coded with as much detail as possible and in compliance with guidelines set forward by MetaLab (Cite MEtalab). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, experiment design and stimuli, and results. For the present analyses, we focus on the following characteristics: 

1 Mean age reported per group of infants, in days;
2 Native language;
3 Size of mispronunciation, measured in features changed;
4 Type of mispronunciation: consonant, vowel, or tone;
5 Dependent variable: Either of the following, capturing infants' reaction to a given naming event (either mispronounced or correct): a) pre-post naming effect: calculated post - pre to give one value, typically compared to chance of 0 or to naming effect of another condition; b) pre-post: comparison of pre-naming and post-naming values; c) post = calculated for post-naming, typically compared to chance of 50%;
6 Condition: Were words mispronounced or not.


[Rewrite this section]
Each row in the database is a set of data that could give rise to an effect size. A given paper could appear in more than one row. This happened when there were multiple experiments, when there were multiple age groups within a single experiment, and when a unique group of infants was exposed to more than one condition (e.g. consonant versus vowel mispronunciations; Mani & Plunkett, 2007) – provided that results were broken down by experiment/infant group/condition in the source paper. In other words, we coded all outcomes that had been reported separately, and which had unique infant participants and/or method characteristics. For example, if the same infants were tested on two conditions and these were reported separately, then we entered two different rows (even though there was only one group of infants), with their methodological features and unique outcomes. To later unbias our data, we XXXX [Need to decide whether we want multilevel models or median data per participant] We will call each row a record. In all, there were 190 records.

## Data analysis

The effect size we report in the present paper is based on comparison of means, standardized by their variance. The most well-known effect size from this group is Cohen's *d* (Cite cohen). To correct for small sample sizes, we use as dependent variable Hedges' *g* instead of Cohen's *d*. In all cases we computed a first effect size for infants looks to target separated by condition (correct or mispronounced). A mispronunciation effect was then

For XXX papers, we 
[List here the different dependent variables]

[Add something about different analysis windows??]




metafor multilevel approach





# Results

## Descrivtives

Database statistics (N Papers, conditions, infants, age range covered)

## Preliminary Analyses

Funnel plot, pub bias

## Meta-analysis of correct and MP studies

separate models

interaction

plot 

## Moderator analyses

- Competitor type (overlap vs. no overlap; familiar vs. unfamiliar)
- Position of mispronunciation
- Consonant vs. Vowel
- Language (English vs. ?)
- Number of features changed
- type of feature changed?  I doubt we have enough for it...
- Type of dv reported

# Discussion


\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
